Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation

### 2022-12-05 beap_pres_dec2022/beap_pres_dec.tex
Dec 05 finished beap presentation - final beap pres updates

% Title page details: 
\title[BEAP Dec 2022]{Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation} 
\author{Alexander Turco}
\date{\today}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

		  		\begin{block}{} \hyperlink{link1}{Background information} \end{block}
		  		\begin{block}{} Research Questions/Explorations \end{block}
		  		\begin{block}{} Experimental Approach \end{block}
		  		\begin{block}{} Results \end{block}
		  		\begin{block}{} Conclusion and Future Work \end{block}

@@

	% For my Background slides, I will talk about important things such as WHat LCRs are, their evolution, stuff like that
	% SLIDE 3 - WHAT ARE LCRs%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% The graphic for this slide is an image of some output from segA with the parameters in the brackets
	\section{Background}
	\begin{frame}{What are LCR's?}
		\label{link1}

@@

	% SLIDE 4 - I do Not Know if I am including this slide
	% The Graphic for this slide is an  
	% Entropy, which is measured by Shannon's Entropy equation is a measure of compositional complexity which uses the proportion of residue(s)
	% in a subsequence to measure the compositional state of that subseequence - A lower variety of residues = lower entropy 
	\begin{frame}{Shannon's Entropy - MAYBE }

			$H = -L\sum p_i log_2(p_i)$

	%SLIDE 5 - LCR's PRESENT IN UNIQUE WAYS
	\begin{frame}{LCR's Present in Unique Ways }

@@

	%SLIDE 6 LCRs are hypermutable
	% Maybe change the lines from the fly to dashed - as per photo Lauren Sent
	\begin{frame}{LCR's are Hypermutable }

@@

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage2.png} \\~\\
				\caption{\centering \textbf{Polymerase Slips Forward}}
			\end{figure}

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage1.png} \\~\\
				\caption{\centering \textbf{Polymerase Slips Backwards}}
			\end{figure}

@@

	%SLIDE 8 - Why Care About LCR Evolution?
	\begin{frame}{Why Care about LCRs and Their Evolution? }

	\begin{center}	
		\begin{tikzpicture}[node distance=2cm]
			\node[startstop] (1) {Disease};
			\node[startstop, right of=1, xshift=2cm] (2) {Biological Processes};
			\node[startstop, right of=2, xshift=2cm] (3) {Presence in Bacteria};
			\node[startstop, above=2, xshift=4cm, yshift=1cm] (4) {LCR's};

@@

		\footnotetext[3]{\tiny\cite{marjoram2003markov}}	
	\end{frame}

@@

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to the normal distribution \pause
			\item Create a random protein sequence and mutate over many generations using $\theta'$ to generate simulated Dataset $D'$ \pause
			\item Calculate summary statistics for simulated dataset $D'$ \pause
			\item If $d(S',S) \le \epsilon$, go to next step, otherwise stay at $\theta$ and return to 1 \pause
			\item Accept $\theta'$ with probability ?? Ask Brian ab this again lol \pause
			\item Return to step 1
		\end{enumerate}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
	\begin{frame}{Simulation Step - MAYBE}

@@

	%For my Results slides, I will talk about things such as the results I have, But i don't have any right now
	%SLIDE 15%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Results}
	\begin{frame}{Results}

	%For my Concluding slides, I will talk about things such as 
	%SLIDE 16%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Conclusion}
	\begin{frame}{Conclusion/Future Work}

>>>>

% Title page details: 
\title[BEAP Dec 2022]{Estimating Evolutionary Parameters for Protein Low Complexity Regions using an Approximate Bayesian Computation} 
\author{Alexander Turco}
\date{December 5, 2022}
\logo{\includegraphics[height=1cm, width=1cm]{logo.png}}

@@

		  		\begin{block}{} \hyperlink{link1}{Background Information} \end{block}
		  		\begin{block}{} Research Questions/Explorations \end{block}
		  		\begin{block}{} Experimental Approach \end{block}
		  		\begin{block}{} Future Work \end{block}

@@

	% For my Background slides, I will talk about important things such as WHat LCRs are, their evolution, stuff like that
	% SLIDE 3 - WHAT ARE LCRs%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	% The graphic for this slide is an image of some output from segA with the parameters in the brackets
	\section{Background}
	\begin{frame}{What are Low Complexity Regions?}
		\label{link1}

@@

	% SLIDE 4 - I do Not Know if I am including this slide
	% The Graphic for this slide is an  
	% Entropy, which is measured by Shannon's Entropy equation is a measure of compositional complexity which uses the proportion of residue(s)
	% in a subsequence to measure the compositional state of that subseequence - A lower variety of residues = lower entropy 
	%\begin{frame}{Shannon's Entropy - MAYBE }

	%		$H = -L\sum p_i log_2(p_i)$

	%\end{frame}

	%SLIDE 5 - LCR's PRESENT IN UNIQUE WAYS
	\begin{frame}{LCRs Present in Unique Ways }

@@

	%SLIDE 6 LCRs are hypermutable
	% Maybe change the lines from the fly to dashed - as per photo Lauren Sent
	\begin{frame}{LCRs are Hypermutable }

@@

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage2n.png} \\~\\
				\caption{\centering \textbf{Polymerase Slips Forward}}
			\end{figure}

			\column{0.5\textwidth}
			\centering
			\begin{figure}
				\vspace{0.5cm}
				\includegraphics[width=\columnwidth, height=2.5cm]{slippage1n.png} \\~\\
				\caption{\centering \textbf{Polymerase Slips Backwards}}
			\end{figure}

@@

	%SLIDE 8 - Why Care About LCR Evolution?
	\begin{frame}{Why Care about LCRs and their Evolution? }

	\begin{center}	
		\begin{tikzpicture}[node distance=2cm]
			\node[startstop] (1) {Disease};
			\node[startstop, right of=1, xshift=2cm] (2) {Biological Processes};
			\node[startstop, right of=2, xshift=2cm] (3) {Presence in Bacteria};
			\node[startstop, above=2, xshift=4cm, yshift=1cm] (4) {LCRs};

@@

		\footnotetext[4]{\tiny\cite{marjoram2003markov}}	
	\end{frame}

@@

		\begin{enumerate}
			\item Propose a move from $\theta$ to $\theta'$ according to the normal distribution \pause
			\item Create a random protein sequence and mutate over many generations using $\theta'$ to generate simulated Dataset $D'$ \pause
			\item Calculate summary statistics for simulated dataset $D'$ \pause
			\item If $d(S',S) \le \epsilon$, go to next step, otherwise stay at $\theta$ and return to 1 \pause
			\item Accept $\theta'$ \pause
			\item Return to step 1
		\end{enumerate}

@@

	%Slide 14 - Maybe to this slide - Maybe throw in extra slides for reference
	%\begin{frame}{Simulation Step - MAYBE}

	%\end{frame}

	%For my Results slides, I will talk about things such as the results I have, But i don't have any right now
	%SLIDE 15%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\section{Results}
	%\begin{frame}{Results}

	%\end{frame}

	%For my Concluding slides, I will talk about things such as 
	%SLIDE 16%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\section{Future Work}
	\begin{frame}{Future Work}

		\begin{itemize}
			\item Graphical representations of simulation iteration versus parameter values 
			\item Implementation of weighted summary statistics in distance calculation
			\item Adjustment of values such as mean and standard deviation of the proposal distribution

			\centering\includegraphics[width=7cm, height=5cm]{graph.png}

		\end{itemize}

@@

	\section{Acknowledgements}
	\begin{frame}{Acknowledgements}
		\begin{itemize}
			\item Dr. Brian Golding \newline
			\item Sam Long \newline
			\item Zachery Dickson \newline
			\item Johanna Enright
		\end{itemize}
	\end{frame}
